\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{soul}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\copyrightyear{2018} 
\acmYear{2018} 
\setcopyright{acmlicensed}
\acmConference[RecSys Challenge '18]{Proceedings of the ACM Recommender Systems Challenge 2018}{October 2, 2018}{Vancouver, BC, Canada}
\acmBooktitle{Proceedings of the ACM Recommender Systems Challenge 2018 (RecSys Challenge '18), October 2, 2018, Vancouver, BC, Canada}
\acmPrice{15.00}
\acmDOI{10.1145/3267471.3267473}
\acmISBN{978-1-4503-6586-4/18/10}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[RecSys'18]{ACM Recommender Systems}{RecSys Challenge Workshop}{Vancouver, Canada}
%\acmYear{2018}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}


\begin{document}
\title[APC using a hybrid system combining features from text and audio]{Automatic playlist continuation using a hybrid recommender system combining features from text and audio}

%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Andres Ferraro}
\affiliation{%
  \institution{Music Technology Group - Universitat Pompeu Fabra}
  \streetaddress{Roc Boronat 138}
  \city{Barcelona}
  \state{Spain}
  \postcode{08018}
}
\email{andres.ferraro@upf.edu}

\author{Dmitry Bogdanov}
\affiliation{%
  \institution{Music Technology Group - Universitat Pompeu Fabra}
  \streetaddress{Roc Boronat 138}
  \city{Barcelona}
  \state{Spain}
  \postcode{08018}
}
\email{dmitry.bogdanov@upf.edu}

\author{Jisang Yoon}
\affiliation{%
  \institution{Kakao Corp.}
  \country{Korea}
}
\email{jason.yoon@kakaocorp.com}

\author{KwangSeob Kim}
\affiliation{%
  \institution{Kakao Corp.}
  \country{Korea}
}
\email{lucas.kim@kakaocorp.com}

\author{Xavier Serra}
\affiliation{%
  \institution{Music Technology Group - Universitat Pompeu Fabra}
  \streetaddress{Roc Boronat 138}
  \city{Barcelona}
  \state{Spain}
  \postcode{08018}
}
\email{xavier.serra@upf.edu}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{A. Ferraro et al.}


\begin{abstract}
The ACM RecSys Challenge 2018 focuses on music recommendation in the context of automatic playlist continuation. In this paper, we describe our approach to the problem and the final hybrid system that was submitted to the challenge by our team Cocoplaya. This system consists in combining the recommendations produced by two different models using ranking fusion. The first model is based on Matrix Factorization and it incorporates information from tracks' audio and playlist titles. The second model generates recommendations based on typical track co-occurrences considering their proximity in the playlists. The proposed approach is efficient and achieves a good overall performance, with our model ranked 4th on the creative track of the challenge leaderboard.
% * <jason.yoon@kakaocorp.com> 2018-07-13T04:06:34.718Z:
%
% ^.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003317.10003347.10003350</concept_id>
<concept_desc>Information systems~Recommender systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003317.10003347.10003352</concept_id>
<concept_desc>Information systems~Information extraction</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003317.10003371.10003386.10003390</concept_id>
<concept_desc>Information systems~Music retrieval</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Recommender systems}
\ccsdesc[300]{Information systems~Information extraction}
\ccsdesc[300]{Information systems~Music retrieval}

\keywords{music recommender systems, automatic playlist continuation, collaborative filtering, content-aware recommendation, challenges}


\maketitle
\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
